01_pca

### 2019-04-24 analysis/01_pca_all.Rmd
more work on spanish translations

```{r setup}
library(tidyverse)
library(ggfortify) # for PCA analysis
library(cluster)
library(cowplot)

@@

en <- p + labs(subtitle = "PCA plot in English") +
  scale_colour_discrete(name = "colour", labels = c("pink", "green", "blue")) +
  scale_shape_discrete(name = "shape", labels = c("circle", "square")) +
  theme_rmh()

es <- p + labs(subtitle = "PCA plot en español") +
  scale_colour_discrete(name = "color", labels = c("rosado", "verde", "azul")) +
  scale_shape_discrete(name = "forma", labels = c("circulo", "triangulo")) +
  theme_rmh()

>>>>

```{r setup}
library(tidyverse)
library(ggfortify) # for PCA analysis
library(cluster)
library(cowplot)
library(stringr)

@@

en <- p + labs(subtitle = "Principle Component Analysis") +
  scale_colour_discrete(name = "tissue", labels = c("hypothalamus", "pituitary", "gonad")) +
  scale_shape_discrete(name = "sex", labels = c("female", "male")) +
  xlab(stringr::str_replace(p$labels$x, "PC", "Principle Component ")) +
  ylab(stringr::str_replace(p$labels$y, "PC", "Principle Component ")) +
  theme_rmh() + guides(colour = guide_legend(order = 2), 
              shape = guide_legend(order = 1))

es <- p + labs(subtitle = "Análisis de Componentes Principales ") +
  scale_colour_discrete(name = "tejido", labels = c("hipotálamo", "pituitaria", "gónada")) +
  scale_shape_discrete(name = "sexo", labels = c("femenino", "masculino")) +
  xlab(stringr::str_replace(p$labels$x, "PC", "Componente Principal ")) +
  ylab(stringr::str_replace(p$labels$y, "PC", "Componente Principal ")) +
  theme_rmh() + guides(colour = guide_legend(order = 2), 
              shape = guide_legend(order = 1))
